An elaborate data set on human gait and the effect of mechanical perturbations

### 2015-03-15 paper.tex
Added commanded data zenodo citation and source file names in captions for m files.

\subsection*{Perturbation Signals}
%
As previously described, the protocol included a phase of normal walking,
followed by longitudinal belt speed perturbations, and ended with a second
segment of normal walking. Three pseudo-random belt speed control signals, with
mean velocities of \SIlist{0.8;1.2;1.6}{\meter\per\second}, were pre-generated
with MATLAB and Simulink (Mathworks, Natick, Massachusetts, USA). The same
control signal was used for all trials at that given speed.

@@

Figure~\ref{fig:input_output} gives an idea of the effect of the treadmill and
controller dynamics by plotting the measured speed of the treadmill belts from
loaded trials (76, 77, 78) against the commanded treadmill control input
signal. The system introduces a delay and seems to act as a low pass filter.
The standard deviations of the measured speeds do not significantly differ from
the desired values: \SIlist{0.05;0.12;0.2}{\meter\per\second} for the three
speeds, respectively.
%
\begin{figure}
  \centering
  \includegraphics{figures/input_vs_output.pdf}
  \caption{Commanded treadmill belt speed (red) and the recorded
    speed (blue) for average belt speeds of
    \SIlist{0.8;1.2;1.6}{\meter\per\second}, respectively.}
  \label{fig:input_output}
\end{figure}

Figure~\ref{fig:freq_analysis} gives a frequency domain view of the effects of
the treadmill dynamics. These spectral density plots were created by averaging
a spectrogram of a twenty second Hamming window. For all speeds, the frequency
content of the commanded and measured time series show similarity below
4~\si{\hertz} and attenuation in the measured spectral density above
4~\si{\hertz}.
%
\begin{figure}
  \centering
  \includegraphics{figures/frequency_analysis.pdf}
  \caption{Power spectral density of the commanded treadmill belt speed
    (red) and the recorded speed (blue) for average belt speeds of
    \SIlist{0.8;1.2;1.6}{\meter\per\second}, respectively}
  \label{fig:freq_analysis}
\end{figure}

@@

In addition to the longitudinal perturbations, lateral perturbations were also
prescribed for a duration of four minutes for one subject in earlier trials
(6,7,8). Figure~\ref{fig:lateral_perturbation} shows the effect of the lateral
control of the treadmill by plotting the commanded and measured treadmill
positions. These signals were generated in a similar manner using MATLAB and
Simulink in which a Gaussian white noise block that twice integrated to obtain
the lateral position. The signal was then high-pass filtered with a
second-order Butterworth filter to eliminate drift and then saturated so that
the signal remained within the 5~\si{\centi\meter} lateral range of the
physical hardware.  The same perturbation signal was used for each of the three
trials.
%
\begin{figure}
  \centering
  \includegraphics{figures/lateral_perturbation.pdf}
  \caption{Commanded treadmill lateral deviation (red) and the recorded
    deviation (blue) for the trials 6, 7, and 8.}
  \label{fig:lateral_perturbation}
\end{figure}

>>>>

\subsection*{Perturbation Signals}
%
As previously described, the protocol included a phase of normal walking,
followed by longitudinal belt speed perturbations, and ended with a second
segment of normal walking. Three pseudo-random belt speed control signals, with
mean velocities of \SIlist{0.8;1.2;1.6}{\meter\per\second}, were pre-generated
with MATLAB and Simulink (Mathworks, Natick, Massachusetts, USA) and are
available for download from Zenodo~\citep{Hnat2015}. The same control signal
was used for all trials at that given speed.

@@

Figure~\ref{fig:input_output} gives an idea of the effect of the treadmill and
controller dynamics by plotting the measured speed of the treadmill belts from
loaded trials (76, 77, 78) against the commanded treadmill control input
signal. The system introduces a delay and seems to act as a low pass filter.
The standard deviations of the measured speeds do not significantly differ from
the desired values: \SIlist{0.05;0.12;0.2}{\meter\per\second} for the three
speeds, respectively.
%
\begin{figure}
  \centering
  \includegraphics{figures/input_vs_output.pdf}
  \cprotect\caption{Commanded treadmill belt speed (red) and the recorded speed
    (blue) for average belt speeds of \SIlist{0.8;1.2;1.6}{\meter\per\second},
    respectively. Generated by \verb|src/input_output_plot.m|.}
  \label{fig:input_output}
\end{figure}

Figure~\ref{fig:freq_analysis} gives a frequency domain view of the effects of
the treadmill dynamics. These spectral density plots were created by averaging
a spectrogram of a twenty second Hamming window. For all speeds, the frequency
content of the commanded and measured time series show similarity below
4~\si{\hertz} and attenuation in the measured spectral density above
4~\si{\hertz}.
%
\begin{figure}
  \centering
  \includegraphics{figures/frequency_analysis.pdf}
  \cprotect\caption{Power spectral density of the commanded treadmill belt
    speed (red) and the recorded speed (blue) for average belt speeds of
    \SIlist{0.8;1.2;1.6}{\meter\per\second}, respectively. Generated by
    \verb|src/frequency_analysis.m|.}
  \label{fig:freq_analysis}
\end{figure}

@@

In addition to the longitudinal perturbations, lateral perturbations were also
prescribed for a duration of four minutes for one subject in earlier trials
(6,7,8). Figure~\ref{fig:lateral_perturbation} shows the effect of the lateral
control of the treadmill by plotting the commanded and measured treadmill
positions. These signals were generated in a similar manner using MATLAB and
Simulink in which a Gaussian white noise block that twice integrated to obtain
the lateral position. The signal was then high-pass filtered with a
second-order Butterworth filter to eliminate drift and then saturated so that
the signal remained within the 5~\si{\centi\meter} lateral range of the
physical hardware.  The same perturbation signal was used for each of the three
trials.
%
\begin{figure}
  \centering
  \includegraphics{figures/lateral_perturbation.pdf}
  \cprotect\caption{Commanded treadmill lateral deviation (red) and the
    recorded deviation (blue) for the trials 6, 7, and 8. Generated by
    \verb|src/lateral_perturbation_plot.m|.}
  \label{fig:lateral_perturbation}
\end{figure}
